---
title: "TidyVerse Recipe"
author: "Mia Chen"
date: "May 5, 2019"
output: html_document
---

In this assignment, we will practice collaborating around a code project with Github as a class.

Using several TidyVerse packages, and the bad-drivers dataset from fivethirtyeight.com, I'm going to create a programming sample "vignette" that demonstrates how to use the capabilities of ggplot2, dplyr, readr packages with the bad-drivers dataset.

## Load TidyVerse
```{r}
library(tidyverse)
```

## Using readr to read data from a csv file
```{r}
drivers <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/bad-drivers/bad-drivers.csv")
```

```{r}
head(drivers)
```

## Using ggplot2 to visualizae data; with pipe operation %>% from dplyr 
```{r}
drivers %>% ggplot(aes(x=reorder(State, -`Car Insurance Premiums ($)`), y=`Car Insurance Premiums ($)`, fill=State)) + 
  geom_bar(stat = "identity") + 
  guides(fill = FALSE) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

